---
title: "Course Project"
author: "Yaoyu"
date: "2014年09月21日"
output: html_document
---
### 1. This is a classification question and should use supervised learning methods.

### 2. Look into data  
- I use `summary(mydata)` find 101 variables are most missing values. I think these variables are not useful, so I delete them and got 58 variables.  
- These 58 variables should standard
- I use `sapply(mydata, class)` find "user_name" and "new_window" are factor variables and the other are numeric variables.

### 3. Featuer Extraction  
- check the similarity between the numeric variables.  
```{r, eval=FALSE}
M <- abs(cor(train1[, -c(1,4,58)]))
diag(M) <- 0
xg <- which(M > 0.8, arr.ind = T)
length(unique(dimnames(xg)[[1]]))
```

I got 22 variables are highly related and use PCA for these variables.  
```{r, eval=FALSE}
p <- mydata[, unique(dimnames(xg)[[1]])]
library(psych)
fa.parallel(p, fa = "pc", n.iter = 100,
            show.legend = F, main = "Scree plot with parallel analysis")
#select 6 factors
pc<-principal(p, nfactors = 6, score = T, rotate = "varimax")
scores <- pc$score
```

- change factor to number
```{r, eval=FALSE}
user_name <- factor(train1$user_name,labels=c(1:6))
new_window <- factor(train1$new_window, labels=c(1:2))
```

- standardize the  remain variables
```{r, eval=FALSE}
standard <- scale(train1[,  !names(mydata) %in% c(unique(dimnames(xg)[[1]]), 'user_name', 'new_window', 'classe')])

```

- combine all the variables
```{r, eval=FALSE}
newdf <- data.frame(scores, user_name = user_name, new_window = new_window, standard, classe = mydata$classe)
```

### 4. Train Model use Radial SVM method
```{r, eval=FALSE}
library(caret)
set.seed(1)
fitControl <- trainControl(method = "repeatedcv",
                           number = 3,
                           repeats = 1,
                           verboseIter=TRUE)
modelFit <- train(classes ~.,data=newdf, method="svmRadial", trControl = fitControl, verbose=FALSE)
```
### 4. Sample error
I expect the accuracy above 80%
The model's results are:
```{r, eval=FALSE}
       sigma    C  Accuracy     Kappa  AccuracySD     KappaSD
1 0.01532849 0.25 0.8586781 0.8212822 0.006818204 0.008471651
2 0.01532849 0.50 0.8902249 0.8610244 0.005066673 0.006383115
3 0.01532849 1.00 0.9170819 0.8949800 0.008002848 0.010087883
```
I select sigma = 0.0153, C = 1 as tuning parameters

### 5. Predict the test data
```{r, eval=FALSE}
(prediction <- predict(modelFit, testdata))
[1] B A A A A E D B A A B C B A E C A B B B
Levels: A B C D E
```

### 6. Submit the answer
```{r, eval=FALSE}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
answers <- as.character(prediction)
pml_write_files(answers)
```

**The whole code in the [course_project.R](https://github.com/yyy256/course-project/blob/master/course_project.R) file.**
